Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-06-14 doc/manuscript/ESSDmanuscript.Rmd
Update ESSDmanuscript.Rmd
#15

>>>>

For data synthesis projects, compilation can only be useful to the EFDB if they include all the required, along with transparent description on the methodology applied to derive emission factors (or have a brief description and a reference to the original source) and the original emission factor values are present (not modified/rounded).
